A Bayesian Statistical Model Is Able to Predict Target-by-Target Selection Behaviour in a Human Foraging Task

### 2022-11-08 Proofs/vision-1871367-proofreading.tex
proofs

%=================================================================
\documentclass[preprints, article,submit,pdftex,moreauthors]{Definitions/mdpi} 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

@@

%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2022}
\copyrightyear{2022}
%\externaleditor{Academic Editor: Firstname Lastname} % For journal Automation, please change Academic Editor to "Communicated by"
\datereceived{} 
\dateaccepted{} 
\datepublished{} 
%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

@@

%=================================================================
% Full title of the paper (Capitalized)
\Title{A Bayesian statistical model is able to predict target-by-target selection behaviour in a human foraging task}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Title}

@@

% Authors, for the paper (add full first names)
\Author{Alasdair D.F. Clarke $^{1}$\orcidA{}, Amelia R. Hunt $^{2}$\orcidB{} and Anna E. Hughes\orcidC{} $^{1,}$*}

%\longauthorlist{yes}

@@

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Clarke, A.D.F.; Hunt, A.; Hughes, A.E.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Psychology, University of Essex, Wivenhoe Park, Colchester, UK, CO4 3SQ\\
$^{2}$ \quad School of Psychology, University of Aberdeen, King's College, Aberdeen, UK, AB24 3FX}

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Foraging refers to search involving multiple targets or multiple types of targets, and as a model task has a long history in animal behaviour and human cognition research. Foraging behaviour is usually operationalized using summary statistics, such as average distance covered during target collection (the path length) and the frequency of switching between target types. We recently introduced an alternative approach, which is to model each instance of target selection as random selection without replacement. Our model produces estimates of a set of foraging biases, such as a bias to select closer targets or targets of a particular category. Here we apply this model to predict individual target selection events. We add a new start position bias to the model, and generate foraging paths using the parameters estimated from individual participants’ pre-existing data. The model predicts which target the participant will select next with a range of accuracy from 43\% to 69\% across participants (chance is 11\%). The model therefore explains a substantial proportion of foraging behaviour in this paradigm. The situations where the model makes errors reveal useful information to guide future research on those aspects of foraging that we have not yet explained.}

% Keywords
\keyword{foraging; visual search; bayesian model; decision; strategy.}

@@

Foraging, the act of searching for and gathering multiple targets (such as food), has been studied in both non-human animal contexts \cite{dawkins1971} and in human psychology studies \cite{kristjansson2014}. Foraging engages a wide range of different perceptual, cognitive, decision-related and motor skills, and is an ecologically relevant behaviour for most species, including humans. For these and other reasons, a sustained interest in foraging has developed our understanding of how we search for multiple instances of multiple types of targets. For example, the classic marginal value theorem \cite {charnov1976} is generally good at predicting when an organism will decide to stop searching in a patch and move on to another, based on the finding rate dropping below an expected rate, and taking into account the relative energy costs of traveling between patches versus staying within a patch. There has also been a concerted effort to characterize the spatial patterns of foraging behaviour. The Lévy Walk, for example, has been argued to be a good description of the foraging path many species take when the locations of targets are unknown (e.g. \citep {bartumeus2005}, but see also \citep{benhamou2007}).

Another general principle of foraging is that of the “search image”, which describes the perceptual features that a foraging animal can use to identify targets or classes of targets \cite{Dukas1993}. A limited capacity for complex search images means that dividing attention over more than one kind of potential search target can impede search, particularly when what distinguished targets from distractors is not a simple feature like colour or motion. As a result, foragers tend to search in “runs” of one type of target before switching to another. In humans, this behaviour has been studied using computer-based displays of targets and distractors (e.g. \citep{ kristjansson2014}), in which participants must “collect” targets (by clicking or tapping on them) and ignore distractors. When targets can be identified based on a single, easily distinguishable feature (for example, find all the red and green shapes and ignore the blue and yellow shapes) participants tend to switch frequently between different types of targets, taking a relatively efficient path through the array. In contrast, when targets are defined based on a combination of more than one feature (e.g. find all the red squares and green circles and ignore the red circles and green squares), participants tend to switch far less frequently, often selecting all the targets of one category and then all the targets of the other. Consequently, the path taken to collect the targets is less efficient. In other words, frequent switching between target types limits the distance travelled between targets, while collecting all the targets of each type before switching to the other type sacrifices some efficiency of movement in service of reducing the mental workload.

Different aspects of foraging behaviour, such as the search image and the search path, clearly interact with one another, but most research has tried to understand them separately. In many cases, the pattern of foraging behaviour has been studied using aggregate measures calculated on the level of a trial, such as the mean number of 'runs' (where the same type of target is selected multiple times in a row) or the total number of targets found during the longest run. These summary statistics can provide a broad view of switching behaviour, but they can also be biased by the spatial distribution of target types, and by a forager's preference for one target or another. To address the need for a more precise set of measurements, we recently developed a new model to analyse foraging data, based on a sampling without replacement procedure \cite{clarke2022foraging}. By using this model, we demonstrated that we were able to break down foraging into a number of different cognitive biases, such as a preference to stick to the same target type, or a preference for nearby targets, and used this model to successfully re-analyse data from a number of open access datasets \cite{kristjansson2014, thornton2020, clarke2022, tagu_kristjansson_2021}.

While our model is able to do a good job of allowing us to understand biases at the level of a trial (e.g. conjunction vs. feature search differences \cite{kristjansson2014} or the influence of high value targets compared to low value targets \cite{tagu2020}), we did not originally investigate to what extent our model was able to predict target-by-target behaviour within any given trial. However, as the model is based on target-by-target level information, it is possible for us to use this information to ask: to what extent does our model predict foraging behaviour within a trial? Can it predict exactly which target a participant will pick next? And if the model makes mistakes, can we understand where it is failing, in order to improve our understanding of how human foraging behaviour operates?

@@

We will make use of the foraging model from Clarke et al (2022) \cite{clarke2022foraging}. This treats foraging as a sampling without replacement process in which each item $i$ has probability $p_i$ of being selected as the next target. The $p_i$ depend on four parameters:

\begin{itemize}
    \item $b_A$ - preference for selecting items of type $A$ rather than $B$.
    \item $b_S$ - preference for selecting items of the same type as the previously selected item.
    \item $\sigma_d$ - preference for selecting items close to the previously selected item.
    \item $\sigma_{\theta}$ - preference to keep selecting items along a straight line versus changing direction.
\end{itemize}

These combine to give:

\begin{linenomath}
\begin{equation}
    w_i = g\left(b_at_i + b_sm(t_i, t_{i-1})\right) \times \rho_d(i, i-1) \rho_{\theta}(i, i-1)
\end{equation}
\end{linenomath}

where $t_i = 1$ if item $i$ is of class $A$ and 0 otherwise, and  $m(t_i, t_{i-1}) =1$ if item $i$ is the same class as the previously selected item. $\rho_d$ and $\rho_{\theta}$ measure proximity and the effect of direction:

\begin{linenomath}
\begin{equation}
    \rho_d = e^{-\sigma_dd(i,j)}
\end{equation}
\end{linenomath}

\begin{linenomath}
\begin{equation}
    \rho_{\theta} = e^{-\sigma_d\theta(i,j)}
\end{equation}
\end{linenomath}

$d(i,j)$ is simply the Euclidean distance between items $i$ and $j$, while $\theta$ is defined as:

\begin{linenomath}
\begin{equation}
    \theta(i,j) = \frac{f(\text{atan2}(i, j) - \text{atan2}(i-1, i))}{\pi}
\end{equation}
\end{linenomath}

with $f(\phi_1, \phi_2) = \text{min}((\phi_1 - \phi_2) \% 2\pi, (\phi_2 - \phi_1) \% 2\pi)$ calculating the angular difference. $\text{atan2}$ is the direction of travel from i to j.  This model is implemented in a multi-level framework, allowing each of the four parameters to vary from participant to participant. Further details including priors and full code can be found with \cite{clarke2022foraging}.

Note: while our model returns estimates of full posterior probability distribution for each parameter, to reduce computational complexity and make it easier to compare to the empirical data, we will work with the means of these distributions for our parameter values.

\subsection{Software environment}

We mainly used R v4.2.0 and rStan v2.26.11 \cite{rstan}. For fitting the model to the data from \cite{clarke2022} we used a university computing cluster with R v3.6.3 and rStan v2.19.2.

@@

To assess how well our model can account for behaviour at the level of individual trials, we start by stepping through each trial in the data from Clarke and colleagues \cite{clarke2022}. For each target selection\footnote{Note: for the reasons discussed above, we ignore the initial target selection for now, as the model has very little to say about it. We return to this issue in section 4.}, in each trial, we can estimate how likely each of the remaining items are to be selected using the parameters from our posterior model. As can be seen in Figure \ref{fig:cal}, the model is putting somewhere between 25\% and 75\% of the weight on the target that is selected next, easily outperforming a chance $1/n$ baseline. There are also interesting differences between the two conditions: for example, in the conjunction condition, there is a clear 'jump' around target 20, which probably reflects the tendency for participants to forage in runs, selecting all exemplars of one target and then all exemplars of the other: there is a decrease in accuracy as people switch and then an increase again. We can also see that the model is well calibrated in that the probabilities assigned to the most likely target manage to capture how often that target is actually selected. However, we can see a decrease in accuracy when it comes to how often ``runner-up`` candidate items are selected as our model appears to systematically undervalue these (presumably by putting too much of the probabilistic weight on low chance items).

\begin{figure}[H]
\centering
\includegraphics[width=12 cm]{Figures/qjep_preds.pdf}
\caption{(\textit{top left}) Posterior probabilities for target selections during a visual foraging task. Each dot shows the data from an individual participant, averaged over trials, in the feature condition and the shaded region indicates the interval in which we expect 67\% of participants to fall. The dashed line indicates chance performance. (\textit{top right}) As top left, except showing the conjunction condition. (\textit{bottom left})  Calibration plot for our foraging model. The $x$-axis gives the largest weight assigned by the model while the $y$-axis shows how often that target was actually selected by a human participant. The dashed line here and in the right plot is the identity line. (\textit{bottom right}) This plot shows how often the model selects the 2nd and 3rd ranked items based on the weights assigned by the model.}
\label{fig:cal}
\end{figure}

We summarise accuracy for each person by calculating the mean proportion of times the model assigns the most weight to the item that was then selected for each participant\footnote{This metric isn't perfect as it averages over all target selections within a trial, and these clearly have different baseline probabilities ($2.5\%-100\%$). However, it has the upside of being more intuitive than anything else we could think of.}. These accuracy scores can be compared to our uniform chance baseline that gives a value of $10.9\%$ over the course of a trial. Figure \ref{fig:cal2} hints at some individual differences when it comes to how predictable the model is: we can see a lot of variation in the size of the weights. However, interestingly, we find that this variability can be explained by our model parameters: nearly all of the differences between different participants, as well as the within-participant differences in the feature and conjunction conditions, can be explained by the $bP$ parameter, which is our proximity bias. The model does a better job of predicting which will be selected next when there is a stronger proximity bias (see \textit{Supplementary Materials: Part 1} for more details).

\begin{figure}[H]
\centering
\includegraphics[width=12 cm]{Figures/qjep_indiv_diff.pdf}
\caption{(\textit{left}) Prediction scores for participants. Boxplots show quartile range and the grey lines indicate individual participants. The dots indicate outliers. (\textit{right}) How accuracy of our model varies with the strength of an individual’s \textit{bM}, \textit{bP}, \textit{pA} and \textit{pS} parameters. We can see two clear outlier participants (marked with an X).}
\label{fig:cal2}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=12 cm]{Figures/qjep_ex_paths.pdf}
\caption{(\textit{top}) Two randomly selected trials in which the model does a good job in accounting for human behaviour. The numbers indicate the order the participant selected targets in. Red arrows indicate places where the model prediction deviates from participant behaviour. When participants diverge from the model's prediction, it appears to be due to some form of path-length optimisation. (\textit{bottom}) Two randomly selected examples in which the model does a less good job in accounting for the order in which human participants selected the items.}
\label{fig:qjep_paths}
\end{figure}

For trials in which the model does a worse job of predicting (accuracy <50$\%$) we can see that the human behaviour appears less organised in terms of proximity in general and it seems unlikely that adding some form of path-length optimisation to our model would improve accuracy with these participants. We can see this more clearly in Figure \ref{fig:qjep_path_lengths}: while our model does a good job of capturing the average total path length, there is considerable variation with some participants generating shorter paths and some longer. We can see  that this appears to be systematically related to how well our model can predict behaviour. Interestingly, these poorly predicted example trials appear to have very strong pS biases, collecting all exemplars of one target and then the other: thus, the participants are carrying out a strategy that the model is not capturing well. This fits with conjunction trials being harder for the model to predict, as these trials generally have fewer switches.

\begin{figure}[H]
\centering
\includegraphics[width=12 cm]{Figures/path_length.pdf}
\caption{(\textit{left}) Histogram showing the distribution of the median path lengths for our human participants and model (fitted to each human participant via the random effect structure). (\textit{right}) The relationship between model accuracy and the proportion of trials in which the human participant has a shorter total path length than predicted.}
\label{fig:qjep_path_lengths}
\end{figure}

\section{Improving the model: location of the first target selection}

One weakness of the foraging model by Clarke et al (2022) \cite{clarke2022foraging} is that it makes little attempt to predict which item will be selected first. In this section we aim to improve this by modelling participant bias (or preference) in their choice of initial target selection. Our approach is inspired by previous work on the central bias in scene viewing \cite{clarke_tatler2014, clarke2017}. These studies fit truncated Gaussian distributions to the  $(x,y)$ coordinates of fixation locations. Here we will do similar, and fit beta distributions\footnote{We use beta distributions here as it is difficult to specify a mixture model using truncated Gaussians in Stan. However, beta distributions may well be a more appropriate choice.} to locations of the initial target selections in the visual foraging task.

Figure \ref{fig:qjep_init_sel_hex} shows the distribution of the locations of first target selections. We can see that unlike the central bias in fixations during scene viewing, the distribution of initial target locations appear to be bimodal: while most targets are positioned in the top left hand corner, there is a second smaller distribution of central target selections. This appears to be due to different participants choosing to utilise different strategies rather than within-subject variation. However, we have no evidence that these different initial strategies affect the model parameters in any systematic way (see \textit{Supplementary Materials: Part 1}). We try two different modelling approaches (multi-level and mixture) to assess whether the less complex mixture model is able to account for the patterns of starting positions seen.

\begin{figure}[H]
\centering
\includegraphics[width=12 cm]{Figures/init_sel_hex_plot.pdf}
\caption{Hexagonal heatmaps showing the two-dimensional distribution of the location of initial target selections. Grey areas indicate cells with a count of 0. (\textit{left}) shows the distribution over all initial target selections (i.e. multiple trials per participant) while (\textit{right}) shows the distribution of each participant's median initial selection (i.e. each participant contributes one data point to the graph). }
\label{fig:qjep_init_sel_hex}
\end{figure}

\subsection{Multi-level Modelling Results}

We first consider a multi-level model in which we fit beta distributions to the $x$ and $y$ coordinates of each participant's initial target selections\footnote{Full details of the analysis can be found in the \textit{Supplementary Materials: Part 1}.}:

\begin{equation}
    x_i \sim Beta(a_{x,i}, b_{x,i})
    \label{eq:beta1x}
\end{equation}
\begin{equation}
    y_i \sim Beta(a_{y,i}, b_{y,i})
    \label{eq:beta1y}
\end{equation}

The results are shown in Figure \ref{fig:qjep_init_sel_mdl} and we can clearly see that most participants either have a strong bias to $x=0$ and $y=0$, or a more diffuse central bias.

>>>>

%=================================================================
\documentclass[vision,article,accept,pdftex,moreauthors]{Definitions/mdpi} 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

@@

%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2022}
\copyrightyear{2022}
\externaleditor{Academic Editor:}

\datereceived{01 August 2022} 
\dateaccepted{02 November 2022} 
\datepublished{} 
%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

@@

%=================================================================
% Full title of the paper (Capitalized)
\Title{A Bayesian Statistical Model Is Able to Predict Target-by-Target Selection Behaviour in a Human Foraging Task}

% MDPI internal command: Title for citation in the left column
\TitleCitation{A Bayesian Statistical Model Is Able to Predict Target-by-Target Selection Behaviour in a Human Foraging Task}

@@

% Authors, for the paper (add full first names)
\Author{\hl{Alasdair D.F. Clarke} $^{1,}$\hl{*}\orcidA{}, Amelia R. Hunt $^{2}$\orcidB{} and Anna E. Hughes~\orcidC{} $^{1}$}
%MDPI: Please carefully check the accuracy of names and affiliations. Please make sure the Address information is sorted from subordinate to superior: Center / Laboratory / Group / Programme / Unit < Department / Division / Faculty / Campus / Institute / School < College / University

%MDPI: According to our system, the correct correspondence author is Alasdair Clarke. Please confirm. RESPONSE: Yes, confirmed.
%MDPI:This is an important note to let you know that to protect the privacy of the author's contact information, we will only display the corresponding authors' contact information on the published paper. However, we hope the contact information of the other authors can also be confirmed or corrected during the proofreading stage, which will be recorded in our database to furnish the author's integrated publication history and also contribute to our future communications. RESPONSE: Okay, all confirmed.

@@

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Clarke, A.D.F.; Hunt, A.R.; Hughes, A.E.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Psychology, University of Essex, Wivenhoe Park, Colchester~CO4 3SQ,~UK; \hl{anna.hughes@essex.ac.uk} \\
%MDPI: added the emails from the submitting system, please confirm. RESPONSE: Confirmed.

$^{2}$ \quad School of Psychology, University of Aberdeen, King's College, Aberdeen~AB24 3FX,~UK; \hl{a.hunt@abdn.ac.uk} }

@@

% Abstract (Do not insert blank lines, i.e., \\) 
\abstract{Foraging refers to search involving multiple targets or multiple types of targets, and as a model task has a long history in animal behaviour and human cognition research. Foraging behaviour is usually operationalized using summary statistics, such as average distance covered during target collection (the path length) and the frequency of switching between target types. We recently introduced an alternative approach, which is to model each instance of target selection as random selection without replacement. Our model produces estimates of a set of foraging biases, such as a bias to select closer targets or targets of a particular category. Here we apply this model to predict individual target selection events. We add a new start position bias to the model, and generate foraging paths using the parameters estimated from individual participants’ pre-existing data. The model predicts which target the participant will select next with a range of accuracy from 43\% to 69\% across participants (chance is 11\%). The model therefore explains a substantial proportion of foraging behaviour in this paradigm. The situations where the model makes errors reveal useful information to guide future research on those aspects of foraging that we have not yet explained.}

% Keywords
\keyword{foraging; visual search; bayesian model; decision; strategy}

@@

\hl{Foraging}, the act of searching for and gathering multiple targets (such as food), has been studied in both nonhuman animal contexts \cite{dawkins1971} and in human psychology studies~\cite{kristjansson2014}. Foraging engages a wide range of different perceptual, cognitive, decision-related and motor skills, and is an ecologically relevant behaviour for most species, including humans. For these and other reasons, a sustained interest in foraging has developed our understanding of how we search for multiple instances of multiple types of targets. For example, the classic marginal value theorem \cite {charnov1976} is generally good at predicting when an organism will decide to stop searching in a patch and move on to another, based on the finding rate dropping below an expected rate, and taking into account the relative energy costs of traveling between patches versus staying within a patch. There has also been a concerted effort to characterize the spatial patterns of foraging behaviour. The Lévy Walk, for example, has been argued to be a good description of the foraging path many species take when the locations of targets are unknown (e.g., \citep {bartumeus2005}, but see also \citep{benhamou2007}). %MDPI:Please make sure that all genes and species names as well as all the variables like "p" or "n" are written in italic font. Protein names, Latin words and genera/families should be kept in a normal font. Greek/Latin expressions and non-common foreign words and phrases should NOT be in Italic format.
%MDPI:  Abbreviations need to be defined, on their first mention, once in the Abstract, once in the Main Text, once in Figures' description, and once in the Tables' footer. Abbreviations used as keywords should be defined too.Please check and make sure that this rule is applied through the whole paper.

Another general principle of foraging is that of the “search image”, which describes the perceptual features that a foraging animal can use to identify targets or classes of targets \cite{Dukas1993}. A limited capacity for complex search images means that dividing attention over more than one kind of potential search target can impede search, particularly when what distinguished targets from distractors is not a simple feature like colour or motion. As a result, foragers tend to search in “runs” of one type of target before switching to another. In humans, this behaviour has been studied using computer-based displays of targets and distractors (e.g., \citep{kristjansson2014}), in which participants must “collect” targets (by clicking or tapping on them) and ignore distractors. When targets can be identified based on a single, easily distinguishable feature (for example, find all the red and green shapes and ignore the blue and yellow shapes) participants tend to switch frequently between different types of targets, taking a relatively efficient path through the array. In contrast, when targets are defined based on a combination of more than one feature (e.g., find all the red squares and green circles and ignore the red circles and green squares), participants tend to switch far less frequently, often selecting all the targets of one category and then all the targets of the other. Consequently, the path taken to collect the targets is less efficient. In other words, frequent switching between target types limits the distance travelled between targets, while collecting all the targets of each type before switching to the other type sacrifices some efficiency of movement in service of reducing the mental workload.

Different aspects of foraging behaviour, such as the search image and the search path, clearly interact with one another, but most research has tried to understand them separately. In many cases, the pattern of foraging behaviour has been studied using aggregate measures calculated on the level of a trial, such as the mean number of 'runs' (where the same type of target is selected multiple times in a row) or the total number of targets found during the longest run. These summary statistics can provide a broad view of switching behaviour, but they can also be biased by the spatial distribution of target types, and by a forager's preference for one target or another. To address the need for a more precise set of measurements, we recently developed a new model to analyse foraging data, based on a sampling without replacement procedure \cite{clarke2022foraging}. By using this model, we demonstrated that we were able to break down foraging into a number of different cognitive biases, such as a preference to stick to the same target type, or a preference for nearby targets, and used this model to successfully reanalyse data from a number of open access datasets \cite{kristjansson2014, thornton2022, clarke2022, tagu_kristjansson_2021}.

While our model is able to do a good job of allowing us to understand biases at the level of a trial (e.g., conjunction vs. feature search differences \cite{kristjansson2014} or the influence of high value targets compared to low value targets \cite{tagu2020}), we did not originally investigate to what extent our model was able to predict target-by-target behaviour within any given trial. However, as the model is based on target-by-target level information, it is possible for us to use this information to ask: to what extent does our model predict foraging behaviour within a trial? Can it predict exactly which target a participant will pick next? If the model makes mistakes, can we understand where it is failing, in order to improve our understanding of how human foraging behaviour operates?

@@

We will make use of the foraging model from Clarke et al. (2022) \cite{clarke2022foraging}. This treats foraging as a sampling without replacement process in which each item $i$ has probability $p_i$ of being selected as the next target. The $p_i$ depend on four parameters:

\begin{itemize}
    \item $b_A$---preference for selecting items of type $A$ rather than $B$.
    \item $b_S$---preference for selecting items of the same type as the previously selected item.
    \item $\sigma_d$---preference for selecting items close to the previously selected item.
    \item $\sigma_{\theta}$---preference to keep selecting items along a straight line versus changing direction.
\end{itemize}

These combine to give:
\begin{linenomath}
\begin{equation}
    w_i = g\left(b_at_i + b_sm(t_i, t_{i-1})\right) \times \rho_d(i, i-1) \rho_{\theta}(i, i-1)
\end{equation}
\end{linenomath}
where $t_i = 1$ if item $i$ is of class $A$ and 0 otherwise, and  $m(t_i, t_{i-1}) =1$ if item $i$ is the same class as the previously selected item. $\rho_d$ and $\rho_{\theta}$ measure proximity and the effect of~direction:
\begin{linenomath}
\begin{equation}
    \rho_d = e^{-\sigma_dd(i,j)}
\end{equation}
\end{linenomath}
\begin{linenomath}
\begin{equation}
    \rho_{\theta} = e^{-\sigma_d\theta(i,j)}
\end{equation}
\end{linenomath}
$d(i,j)$ is simply the Euclidean distance between items $i$ and $j$, while $\theta$ is defined as:
\begin{linenomath}
\begin{equation}
    \theta(i,j) = \frac{f(\text{atan2}(i, j) - \text{atan2}(i-1, i))}{\pi}
\end{equation}
\end{linenomath}
with $f(\phi_1, \phi_2) = \text{min}((\phi_1 - \phi_2) \% 2\pi, (\phi_2 - \phi_1) \% 2\pi)$ calculating the angular difference. $\text{atan2}$ is the direction of travel from i to j.  This model is implemented in a multilevel framework, allowing each of the four parameters to vary from participant to participant. Further details including priors and full code can be found with \cite{clarke2022foraging}.

Note: while our model returns estimates of full posterior probability distribution for each parameter, to reduce computational complexity and make it easier to compare to the empirical data, we will work with the means of these distributions for our parameter~values.

\subsection{Software Environment}

We mainly \hl{used} R v4.2.0 and rStan v2.26.11 \cite{rstan} (R Foundation for Statistical Computing, Vienna, Austria). For fitting the model to the data from~\cite{clarke2022} we used a university computing cluster with R v3.6.3 and rStan v2.19.2.%MDPI:For all equipment/software/products used, the following information should be given: company name, city, state abbreviation (if its from USA or Canada), and country must be provided. Please apply this rule through the whole Materials and Methods section

@@

To assess how well our model can account for behaviour at the level of individual trials, we start by stepping through each trial in the data from Clarke and colleagues \cite{clarke2022}. For each target selection \hl{(}Note: for the reasons discussed above, we ignore the initial target selection for now, as the model has very little to say about it. We return to this issue in Section \ref{s4}\hl{)}, %MDPI: footer is not allowed in this type article, we moved it to the (), please confirm. RESPONSE: Confirmed
in each trial, we can estimate how likely each of the remaining items are to be selected using the parameters from our posterior model. As can be seen in Figure \ref{fig:cal}, the model is putting somewhere between 25\% and 75\% of the weight on the target that is selected next, easily outperforming a chance $1/n$ baseline. There are also interesting differences between the two conditions. For example, in the conjunction condition, there is a clear 'jump' around target 20, which probably reflects the tendency for participants to forage in runs, selecting all exemplars of one target and then all exemplars of the other: there is a decrease in accuracy as people switch and then an increase again. We can also see that the model is well calibrated in that the probabilities assigned to the most likely target manage to capture how often that target is actually selected. However, we can see a decrease in accuracy when it comes to how often ``runner-up`` candidate items are selected as our model appears to systematically undervalue these (presumably by putting too much of the probabilistic weight on low chance items).

\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=17.8 cm]{Figures/qjep_preds.pdf}
\end{adjustwidth}
\caption{({\textbf{\hl{top left}}}) Posterior probabilities for target selections during a visual foraging task. Each dot shows the data from an individual participant, averaged over trials, in the feature condition and the shaded region indicates the interval in which we expect 67\% of participants to fall. The dashed line indicates chance performance. (\textbf{\hl{top right}}) As top left, except showing the conjunction condition. (\textbf{\hl{bottom left}})  Calibration plot for our foraging model. The $x$-axis gives the largest weight assigned by the model while the $y$-axis shows how often that target was actually selected by a human participant. The dashed line here and in the right plot is the identity line. (\textbf{\hl{bottom right}}) This plot shows how often the model selects the 2nd and 3rd ranked items based on the weights assigned by the model.} %mdpi: we removed the subfigure label from italic to be not italic and added bold of it according to our rule, please confirm, same in below figures. RESPONSE: Confirmed.

% Also, please divide the figure into 4 subfigures and  note them accordingly. Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole. Subfigures should be provided with sub-caption and put sub-caption in figure caption.

%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors.  If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it. Thank you for your cooperation! RESPONSE: We confirm that all the figures are original.

\label{fig:cal}
\end{figure}

We summarise accuracy for each person by calculating the mean proportion of times the model assigns the most weight to the item that was then selected for each participant \hl{(}This metric isn't perfect as it averages over all target selections within a trial, and these clearly have different baseline probabilities: 2.5--100\%. However, it has the upside of being more intuitive than anything else we could think of\hl{)}. %MDPI: footer is not allowed in this type article, we moved it to the (), please confirm. RESPONSE: Slightly modified, but confirmed.
These accuracy scores can be compared to our uniform chance baseline that gives a value of $10.9\%$ over the course of a trial. Figure \ref{fig:cal2} hints at some individual differences when it comes to how predictable the model is: we can see a lot of variation in the size of the weights. However, interestingly, we find that this variability can be explained by our model parameters: nearly all of the differences between different participants, as well as the within-participant differences in the feature and conjunction conditions, can be explained by the $bP$ parameter, which is our proximity bias. The model does a better job of predicting which will be selected next when there is a stronger proximity bias (see {\hl{Supplementary Materials: Part 1}} for more details).

@@

\begin{figure}[H]
\includegraphics[width=13.5 cm]{Figures/qjep_indiv_diff.pdf}
\caption{({\textbf{\hl{left}}}) Prediction scores for participants. Boxplots show quartile range and the grey lines indicate individual participants. The dots indicate outliers. (\textbf{\hl{right}}) How accuracy of our model varies with the strength of an individual’s \textit{bM}, \textit{bP}, \textit{pA} and \textit{pS} parameters. We can see two clear outlier participants (marked with an X).} %MDPI: please divide the figure into 2 subfigures and  note them accordingly. Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole. Subfigures should be provided with sub-caption and put sub-caption in figure caption.
%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors. If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it.Thank you for your cooperation! RESPONSE: Confirmed.

\label{fig:cal2}
\end{figure}   
\vspace{-12pt}

\begin{figure}[H]
\includegraphics[width=12 cm]{Figures/qjep_ex_paths.pdf}
\caption{(\textbf{\hl{top}}) Two randomly selected trials in which the model does a good job in accounting for human behaviour. The numbers indicate the order the participant selected targets in. Red arrows indicate places where the model prediction deviates from participant behaviour. When participants diverge from the model's prediction, it appears to be due to some form of path-length optimisation. (\textbf{\hl{bottom}}) Two randomly selected examples in which the model does a less good job in accounting for the order in which human participants selected the items.}%MDPI: please divide the figure into subfigures and  note them accordingly. Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole. Subfigures should be provided with sub-caption and put sub-caption in figure caption. Please add explanation for all the symbols/colors
%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors. If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it. Thank you for your cooperation! RESPONSE: Confirmed

\label{fig:qjep_paths}
\end{figure}

For trials in which the model does a worse job of predicting (accuracy <50$\%$) we can see that the human behaviour appears less organised in terms of proximity in general and it seems unlikely that adding some form of path-length optimisation to our model would improve accuracy with these participants. We can see this more clearly in Figure \ref{fig:qjep_path_lengths}: while our model does a good job of capturing the average total path length, there is considerable variation with some participants generating shorter paths and some longer. We can see  that this appears to be systematically related to how well our model can predict behaviour. Interestingly, in some cases, poorly predicted trials appear to have very strong pS biases, collecting all exemplars of one target and then the other: thus, the participants are carrying out a strategy that the model is not capturing well. This fits with conjunction trials being harder for the model to predict, as these trials generally have fewer switches. 
\vspace{-10pt}
\begin{figure}[H]
\includegraphics[width=13.5 cm]{Figures/path_length.pdf}
\caption{({\textbf{\hl{left}}}) Histogram showing the distribution of the median path lengths for our human participants and model (fitted to each human participant via the random effect structure). (\textbf{\hl{right}}) The relationship between model accuracy and the proportion of trials in which the human participant has a shorter total path length than predicted.}%MDPI:please divide the figure into 2 subfigures and  note them accordingly. Subfigures should be numbered by Latin letters with parentheses, e.g., (a), (b), (c), or (A), (B), (C), etc., which should be put below the image or within the image; only Latin letters should be bold; parentheses should be whole. Subfigures should be provided with sub-caption and put sub-caption in figure caption.
%MDPI: Please confirm that all the figures are the original work of this manuscript’s authors. If they have been adapted or they belong to another author/publisher, it’s required to send us the copyright agreement for using it. Thank you for your cooperation! RESPONSE: Confirmed

\label{fig:qjep_path_lengths}
\end{figure}

\section{Improving the Model: Location of the First Target Selection \label{s4}}
